Allocation Removal by Partial Evaluation in a Tracing JIT

### 2010-10-14 talk/pepm2011/paper.tex
try to have a marginally acceptable author block

\documentclass{sigplanconf}

@@

%
\def\sharedaffiliation{%
\end{tabular}
\begin{tabular}{c}}
%
\begin{document}
\conferenceinfo{PEPM'11,} {XXX}
\CopyrightYear{XXX}
\copyrightdata{XXX}

@@

\authorinfo{Carl Friedrich Bolz \and Antonio Cuni \and Maciej Fijałkowski \and Michael Leuschel \and Samuele Pedroni \and Armin Rigo}
           {Heinrich-Heine-Universität Düsseldorf, STUPS Group, Germany XXX}
           {cfbolz@gmx.de, anto.cuni@gmail.com, fijal@merlinux.eu,
           leuschel@cs.uni-duesseldorf.de, samuele.pedroni@gmail.com, arigo@tunes.org}

@@

The authors would like to thank Stefan Hallerstede and Thomas Stiehl for
fruitful discussions during the writing of the paper.

>>>>

\documentclass[preprint]{sigplanconf}

@@

%
\def\sharedaffiliation{%
\end{tabular}
\begin{tabular}{c}}
%
\begin{document}
\conferenceinfo{PEPM}{'11, Austin, USA}
\CopyrightYear{2011}
\copyrightdata{[to be supplied]}

@@

\authorinfo{Carl Friedrich Bolz$^a$ \and Antonio Cuni$^a$ \and Maciej Fijałkowski$^b$ \and Michael Leuschel$^a$ \and \\
            Samuele Pedroni$^c$ \and Armin Rigo$^a$}
           {$^a$Heinrich-Heine-Universität Düsseldorf, STUPS Group, Germany

            $^b$merlinux GmbH, Hildesheim, Germany

            $^c$Open End, Göteborg, Sweden
           }
           {cfbolz@gmx.de, anto.cuni@gmail.com, fijal@merlinux.eu,
           leuschel@cs.uni-duesseldorf.de, samuele.pedroni@gmail.com, arigo@tunes.org}
%           {Heinrich-Heine-Universität Düsseldorf, STUPS Group, Germany} \and {merlinux GmbH, Hildesheim, Germany} \and {Open End, Göteborg, Sweden}

@@

The authors would like to thank Stefan Hallerstede, David Schneider and Thomas
Stiehl for fruitful discussions during the writing of the paper.
